Supplementary material for\\ A Benchmark of Named Entity Recognition Approaches in Historical Documents\\ Application to 19$^{th}$ Century French Directories

### 2022-01-20 src-latex/parts/20-related-work.tex

\subsection{Named Entity Recognition}

@@

Supervised approaches include both approaches implementing supervised learning algorithms with careful text feature engineering, and deep learning based approaches which automatically build their own features to classify tokens into named entity categories.
In recent years, the latter have grown dramatically, yielding state-of-the-art performances as shown in the recent survey proposed by \cite{li2020}. This survey concludes that fine-tuning general-purpose contextualized language models with domain-specific data is very likely to give good performance for use cases with domain-specific texts and few training data. This strategy has been adopted by \cite{Labusch2020NamedED} to extract named entities in OCRed historical texts in German, French, and English. However, the NER performance decreased dramatically with OCRed texts is noted, especially for the English texts for which the OCR is of poorer quality.

\subsection{Improving Named Entity Recognition in historical texts}
\label{subsection:stoa-ner-on-historical-texts}

Several recent studies have focused on the extent to which the quality of the OCR affects the results produced by a NER model.
\cite{van2020assessing} assess the impact of OCR on several NLP downstream tasks, including NER. They worked on a corpus published by a post-OCR correction software company, made of many journal articles with different levels of OCR errors and their respective ground truths.
For each OCRed article, the Word Error Rate (WER) is computed and the English model \textit{en-core-web-lg} provided by Spacy\footnote{\url{https://spacy.io/}} library is used to perform NER on \textit{Person}, \textit{GPE}\footnote{Geopolitical Entity} and \textit{Date}.
The performance of the NER model with respect to OCR quality is eventually assessed by computing the F-measure for each NER class, and each article i.e., each WER value.
\cite{hamdi2020assessing} performed a similar but more extensive evaluation on four different NER models: CoreNLP using Conditional Random Fields and three deep neural models, BLSTM-CNN, BLSTM-CRF, and BLSTM-CNN-CRF.
They tested them on two well-known NER benchmark corpora: CoNLL-02 and CoNLL-03. They applied four different types of OCR noise to each corpus, with two levels of degradation and computed the WER and Character Error Rate (CER) for each degraded version.
Finally, they applied each NER model to the progressively degraded versions of the corpus and computed the resulting F-measure.
Overall, NER F-measure drops from 90\% to 50\% when the WER increase from 8\% to 50\%. However, models based on deep neural networks seem less sensitive to OCR errors.

>>>>

\subsection{Named Entity Recognition in historical texts}
\label{subsection:stoa-ner-on-historical-texts}

@@

Supervised approaches include both approaches implementing supervised learning algorithms with careful text feature engineering, and deep learning based approaches which automatically build their own features to classify tokens into named entity categories.
In recent years, the latter have grown dramatically, yielding state-of-the-art performances as shown in the recent survey proposed by \cite{li2020}. This survey concludes that fine-tuning general-purpose contextualized language models with domain-specific data is very likely to give good performance for use cases with domain-specific texts and few training data. This strategy has been adopted by \cite{Labusch2020NamedED} to extract named entities in OCRed historical texts in German, French, and English. However, the NER performance decreased dramatically for OCRed texts compared to the groundtruth dataset. This decrease went hand in hand with the drop of the OCR quality. 
Several recent studies have focused on the extent to which the quality of the OCR affects the results produced by a NER model.
\cite{van2020assessing} assess the impact of OCR on several NLP downstream tasks, including NER. They worked on a corpus published by a post-OCR correction software company, made of many journal articles with different levels of OCR errors and their respective ground truths.
For each OCRed article, the Word Error Rate (WER) is computed and the English model \textit{en-core-web-lg} provided by Spacy\footnote{\url{https://spacy.io/}} library is used to perform NER on \textit{Person}, \textit{GPE}\footnote{Geopolitical Entity} and \textit{Date}.
The performance of the NER model with respect to OCR quality is eventually assessed by computing the F-measure for each NER class, and each article i.e., each WER value.
\cite{hamdi2020assessing} performed a similar but more extensive evaluation on four different NER models: CoreNLP using Conditional Random Fields and three deep neural models, BLSTM-CNN, BLSTM-CRF, and BLSTM-CNN-CRF.
They tested them on two well-known NER benchmark corpora: CoNLL-02 and CoNLL-03. They applied four different types of OCR noise to each corpus, with two levels of degradation and computed the WER and Character Error Rate (CER) for each degraded version.
Finally, they applied each NER model to the progressively degraded versions of the corpus and computed the resulting F-measure.
Overall, NER F-measure drops from 90\% to 50\% when the WER increase from 8\% to 50\%. However, models based on deep neural networks seem less sensitive to OCR errors.
